% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{gensymb}
\usepackage{enumitem}
% no space above enumerate
\setlist{nolistsep}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}
\setlist[itemize]{itemsep=0.2em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 & #2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

%\parskip=0.1em
%\usepackage[parfill]{parskip}
% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Randy J. Westlund, E.I.}}

28 Princeton St Apt 2 \ \ \textbullet \ \ Medford, MA 02155 \\
(704) 526-5337 \ \ \textbullet
\ \ rwestlun@gmail.com \ \ \textbullet
\ \ www.textplain.net
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Education}
\begin{itemize*}
	\parskip=0.1em
	\item 
	\headerrow
		{\textbf{The University of North Carolina at Charlotte}}
		{\textbf{Charlotte, NC}}
	\\
	\headerrow
		{\emph{B.S., Computer Engineering}}
		{\emph{2007 -- 2011}}
	\headerrow
		{\emph{Minor: Mathematics, Classical Studies}}
		{\emph{2011}}
        \emph{Major GPA: 3.70, Overall GPA: 3.56} \\
        \textbf{Senior Design Project}
        \begin{itemize*}
            \item Won second place of 50 teams, leading an interdisciplinary
                team of 5 engineering seniors on a two-semester project to
                design and build an autonomous robot with obstacle avoidance
                and a user-controlled videoconference mode. The robot ran
                Gentoo Linux on a Pandaboard (cross compiled for ARM), with
                Robot Operating System (ROS). Ultrasonic, IR range, and bump
                sensors provided safety. A Kinect was used for computer vision
                with the Point Cloud Library.
        \end{itemize*}
    \textbf{Course Projects}
    \begin{itemize*}
        \item Worked in teams to design embedded computer systems in C.
            Individually wrote a custom version of malloc()/free() and
            implemented it on a Renesas microcontroller.

        \item Implemented a parallelized, pipelined version of the
            Needleman-Wunsch algorithm for global sequence alignment of A-C-G-T
            protein sequences in VHDL\@.  Working solo, I outperformed teams of
            grad students.  The professor asked to use my presentation for
            himself.

        \item Implemented 3D graphics rendering algorithms of Lambertian and
            specular surfaces with the Phong Reflection Model in MATLAB and
            rendered simple shapes in Java 3D.

        \item Worked in teams to design, prepare, and present a 70-page formal
            business proposal for an original idea in a hypothetical start-up
            company.

        \item Individually designed, simulated, and constructed a four-stage 60
            dB amplifier with BJTs.

        \item Worked in teams to design and process RFID antennas on 4” silicon
            wafers in a clean room.
    \end{itemize*}
\end{itemize*}

\hrule
\vspace{-0.4em}

\subsection*{Professional Accomplishments}
\headerrow
    {\textbf{Engineer Intern}, North Carolina, FE Certificate Number A-26823}
    {\emph{December 2011}}
\headerrow
    {\textbf{Second Place}, UNC Charlotte Engineering Senior Design Competition}
    {\emph{December 2011}}
\headerrow
    {\textbf{FCC Amateur Radio License}, General Class KK4DOP}
    {\emph{August 2011}}

\hrule
\vspace{-0.4em}
\subsection*{Experience}
\begin{itemize}
	\parskip=0.1em
    \item
    \headerrow
        {\textbf{EAPS, Massachusetts Institute of Technology}}
        {\textbf{Cambridge, MA}}
    \headerrow
        {\emph{System Architect, Researcher}}
        {\emph{April 2014 -- Present}}
    \begin{itemize}
        \item Took the primary role in developing SLOOP, a pattern retrieval
            engine for animal biometrics that uses cloud computing, machine
            learning, and crowd sourcing to greatly improve the study of animal
            movement and behavior.  SLOOP takes any number of images (tens to
            tens of thousands) of a particular species of animal and applies
            pattern recognition to identify the individual in the image.  User
            feedback improves the system's matching process.  This type of
            human-in-the-loop processing provides scientists with a
            non-invasive way to track individuals and model animal populations
            over time.

        \item Independently redesigned the system from the ground up,
            implementing a new RESTful system from scratch using Node.js on the
            back end and Angular.js and Bootstrap on the front end to manage
            the new high-performance client-side application.  The system
            performs well on both desktop and mobile platforms.  Moved all data
            from the filesystem to the ACID-compliant PostgreSQL relational
            database.

        \item Expanded the system to handle new species, implemented a web
            interface management console, and packaged it in a deployable
            virtual machine.

        \item Made trips to Mexico to test unmanned aerial systems (UAS) at
            Popocatépetl, an active volcano. The goal was to fly sensors
            through the volcano's plume in order to collect important
            environmental data.

        \item Cross compiled and deployed a custom NanoBSD image to ALIX x86
            embedded boards to provide communications over 900 MHz between the
            UAS and the ground.

        \item Implemented a realtime H.264 video streaming solution and live
            telemetry feed from the UAS to the ground.
    \end{itemize}

	\item
	\headerrow
		{\textbf{Charlotte Tent and Awning Co., Inc.}}
		{\textbf{Charlotte, NC}}
	\headerrow
		{\emph{Database Administrator \& Efficiency Evaluator}}
        {\emph{March 2013 - Present}}
	\begin{itemize}
        \item Led business meetings with management to study paper-driven
            company workflow and discuss areas where technology could improve
            efficiency and communication in the company.  Because every awning
            is custom made with unique specifications, there are unique
            workflow challenges to address.

        \item Designed data schemas in MongoDB and developed an early prototype
            database server and counterpart C\#.NET desktop application to
            demonstrate the capabilities of a possible database engineered
            specifically to meet the unique needs of the company.  This system
            helped manage customers and jobs.

        \item Led follow up meetings with management to discuss the impact of
            the prototype and what we had learned about the company's needs.
            After determining that real time mobile access was necessary,
            redesigned the front end and implemented a MEAN stack and
            client-side application with Node.js and Angular.js.  Utilized
            MongoDB local and remote replication to ensure data integrity.  Led
            seminars for employees and management for each major version change
            and handled support emails.

        \item With a mobile-first development model, expanded the system over
            time to include the means to manage customers, job status and
            versioning, authentication and authorization with OAuth, salesman
            appointments, file uploads, and data reporting and analysis of
            information.  With the power of secure, access-controlled, and
            always up-to-date company records at their fingertips wherever they
            go, the company's productivity has increased beyond initial
            projections.
	\end{itemize}

	\headerrow
		{\emph{Bookkeeper/Assistant}}
		{\emph{June 2005 -- September 2009}}
	\begin{itemize}
        \item Responsible for overseeing cash flow of company including
            invoicing of customers and accounts payable of corporation with
            \$2.5 million in annual revenues.

        \item Directly interacted with company owner and salespersons to ensure
            efficient workflow of sales orders from initial proposal through
            project completion.

        \item Assisted in design, build, and setup of trade shows convention
            displays for groups of 20,000 -- 30,000 attendees.
	\end{itemize}

    \item
    \headerrow
		{\textbf{E5 Aeronautics}}
		{\textbf{Cambridge, MA}}
	\headerrow
		{\emph{Systems Engineer}}
		{\emph{July 2013 -- May 2014}}
    \begin{itemize}
        \item Designed embedded systems and communication protocols for small
            unmanned aircraft for civilian use.  Primary use cases include
            mapping, wildlife monitoring, and volcano plume sampling.  Explored
            issues such as mesh networking, low-latency remote control, and
            redundant sensor systems.  Used MAVLink and custom communication
            protocols.

        \item Modified firmware for Wi-Fi SD cards and Canon cameras with CHDK,
            wrote custom device drivers for 900 MHz radios, and deployed to an
            embedded Linux development board.  Utilized memory-mapped files to
            meet near realtime message passing requirements.
    \end{itemize}

    \item
    \headerrow
		{\textbf{Urban Scholars, University of Massachusetts Boston}}
		{\textbf{Boston, MA}}
	\headerrow
		{\emph{Robotics Instructor}}
		{\emph{June 2013 -- December 2013}}
	\begin{itemize}
        \item Participated as an instructor in the Urban Scholars program,
            which assists academically advanced but economically disadvantaged
            or first-generation college bound high school and middle school
            students.  The program provides afternoon classes, summer school,
            and tutoring, to assist students with making it to college.
            Students in good standing are paid a stipend to enable them to
            spend time learning rather than working.

        \item Designed and proposed my own courses on Beginning Robotics,
            Advanced Robotics, and Intro Programming, working them in with the
            new Common Core standards for a balanced curriculum.  Met weekly
            with the academic coordinator to discuss lesson plans and improve
            my teaching skills.

        \item Taught classes of 15 - 25 students from ages 11 - 16.  Topics
            included Lego Mindstorms, custom tank robots with Arduinos and a
            Pololu gearbox, Java programming, how computers think, security and
            encryption, internet safely, robotics in the news, ethical
            considerations, important men and women in robotics and computing,
            and reflective writing.
	\end{itemize}

	\item
	\headerrow
		{\textbf{SPI Team, LLC}}
		{\textbf{Highland, MD}}
	\headerrow
		{\emph{Start-up Company Founder \& Lead Engineer}}
		{\emph{February 2012 -- June 2013}}
	\begin{itemize}
        \item Started a business with my retired mentor from NASA\@.  I helped
            organize the company, including financial records and professional
            contacts, and helped build a small team of skilled engineers.  I
            worked to keep the team on-task and divided work appropriately.

        \item With a team, designed and implemented a prototype electronics box
            to control robotic arms with inverse kinematic endpoint control and
            PID feedback loops.  These arms used a variety of devices,
            including servos, DC motors, potentiometers, magnetic and absolute
            encoders, and linear actuators.  The control algorithm was
            developed on a Maple development board after being prototyped in
            Python.  These control boxes may see military service soon.  I
            designed the circuit, wrote the low-level I/O functions to enable
            the microcontroller to communicate with the sensors and motors, and
            helped solve the inverse kinematic equations.

        \item Made business plans with a patent holder for a germicidal UVC
            light device, and designed a prototype with a team. The device is
            an embedded light fixture containing a UVC bulb and moving shutter
            that can alternately sanitize the air or irradiate the surfaces in
            the room if it detects that no one is present.  The prototype used
            an assortment of sensors and 802.15.4 wireless mesh communication.
            Personally wrote the embedded firmware and designed a communication
            protocol.  Deliverables included the prototype device, prototype
            control software, and engineering documentation.

            % Changed to make Ann happy.
        %\item Made business plans with Elevated Health Systems LLC, a patent
            %holder for a germicidal UVC light device, and designed a prototype
            %with a team. The device is an embedded light fixture containing a
            %UVC bulb and moving shutter that can alternately sanitize the air
            %or irradiate the surfaces in the room if it detects that no one is
            %present.  The prototype used an assortment of sensors and 802.15.4
            %wireless mesh communication.  Personally wrote the embedded
            %firmware and designed a communication protocol.  Deliverables
            %included the prototype device, prototype control software, and
            %engineering documentation.  See US patents 7692172 and 8097861.

        \item Under a new contract, continued work on a software-defined radio
            project in McMurdo, Antarctica that I started for NASA with NOAA's
            POES satellites during the summer of 2011 (see Goddard Space Flight
            Center, below).  I returned to Antarctica in December 2012 to
            verify that my system was functional, record data, and retrograde
            the 28-year old ground station.  All equipment was tested and
            packaged for return to NASA Goddard.  The ground station was
            prepared for a new team of NASA engineers.
	\end{itemize}

	\item
	\headerrow
		{\textbf{NASA Goddard Space Flight Center}}
		{\textbf{Greenbelt, MD}}
	\\
	\headerrow
		{\emph{Apprentice/Lead Intern, Robotics Engineering Boot Camp}}
		{\emph{June 2011 -- Aug 2011}}
	\begin{itemize}
        \item Arrived early and familiarized myself with current projects.
            When other interns arrived, gave presentations to them and assisted
            in dividing work based on individual strengths.  Coordinated group
            work and managed all contact information.

        \item Started a project using a Universal Software Radio Peripheral
            (USRP) with GNU Radio to design and implement a software-defined
            radio for the NASA Antarctic Interactive Launch Support (NAILS)
            system at the NASA Satellite Ground Station in McMurdo, Antarctica.
            The system replaces outdated analog signal processing equipment to
            receive, demodulate, and decode L-band and S-band satellite
            communications from NOAA's Polar Operational Environmental
            Satellites (POES).  I personally installed a \$6,000 Linux server
            and my software-defined radio in the NAILS server racks during a
            trip to McMurdo in December 2011 with a small team of NASA
            engineers.  I returned in December 2012 to continue work (see SPI
            Team, above).

        \item Coordinated the LIDAR-Assisted Robotic Group Exploration (LARGE)
            project, using multiple robots with 3D SLAM to generate cohesive
            mapping data.  The robots ran ROS and took input from a 360\degree\
            LIDAR, a Kinect, quadrature encoders, and laser rangefinders.  Main
            software challenges include image stitching, navigation, obstacle
            avoidance, and directing multiple specialized workerbots from the
            mothership.  Robotic arms were being developed in parallel.  The
            goal of the project was to demonstrate the viability of
            implementation on Mars and other planets.
	\end{itemize}
\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Core Technical Skills}
\begin{itemize*}
    \item \textbf{Programming Languages:} C, \CPP, Java, C\#, Perl,
            Python, JavaScript
    \item \textbf{Domain-Specific:} VHDL, SQL, GNU Make, Shell, Regular
            Expressions, HTML/CSS, \LaTeX, Octave/MATLAB
    \item \textbf{Operating Systems and Programs}
        \begin{itemize*}
            \item Linux, GCC/GDB, Custom kernels and drivers, memory-mapped files
            \item FreeBSD, Jails, ZFS
            \item Windows, Visual Studio, QuickBooks
            \item Xilinx ISE
        \end{itemize*}
    \item \textbf{System Administration}
        \begin{itemize*}
            \item Familiarity with server racks and enterprise hardware
            \item Software RAID, LUKS encryption, ZRAID
            \item Experience managing multiple small home servers with varying
                operating systems
            \item Apache, Nginx, PostgreSQL, MongoDB
            \item Proper password management
        \end{itemize*}
    \item \textbf{Frameworks}
        \begin{itemize*}
            \item \textbf{Web:} Django, Node.js, Express, Angular.js, Bootstrap,
                    jQuery, OAuth
            \item \textbf{Robotics:} Robot Operating System (ROS), MAVLink
            \item \textbf{Version Control:} SVN, Git, CVS
            \item \textbf{Libraries:} .NET, Qt, STL, Ncurses
        \end{itemize*}
    \item \textbf{Embedded Systems \& Electronics}
        \begin{itemize*}
            \item Arduino, AVR, BeagleBone, Misc ARM and x86 dev boards
            \item Efficient use of on-chip peripherals
            \item UART, SPI, I$^2$C/TWI protocols
            \item Command line cross compiler toolchains built from source
            \item Circuit design and home etching with Eagle and KiCad EDA software
            \item Soldering and prototyping, use of electronics workbench
            \item Sourcing parts from suppliers like Digi-Key and Mouser
        \end{itemize*}
    \item \textbf{RF Communications}
        \begin{itemize*}
            \item Digital Signal Processing in GNU Radio and MATLAB
            \item Universal Software Radio Peripheral (USRP)
            \item Amateur Radio
            \item Processing from feedpoint to baseband and demodulation
            \item Mesh networking
        \end{itemize*}
    \item \textbf{Peripheral Hardware}
        \begin{itemize*}
            \item Kinect, LIDAR systems
            \item Ultrasonic and IR rangefinders
            \item Servos, DC motors, linear actuators, encoders
            \item 802.15.4 XBee radios
            \item Canon cameras and CHDK
        \end{itemize*}
    \item \textbf{Foreign Languages}
        \begin{itemize*}
            \item Latin: Two years of study
            \item Ancient (Attic) Greek: One year of study
            \item Spanish: Two years of study
        \end{itemize*}
    \item \textbf{Miscellaneous}
        \begin{itemize*}
            \item Leadership and project management
            \item Formal and written business communication
            \item Detailed documentation practices
            \item Antarctic survival and igloo design
        \end{itemize*}
\end{itemize*}

\hrule
\vspace{-0.4em}
\subsection*{Projects}
    \begin{itemize}
        \item \headerrow{\textbf{Textplain}}{\emph{April 2015}}
        \begin{itemize}
            \item Built a personal website without a CMS using Django,
                PostgreSQL, and Nginx.  The site avoids the use of client-side
                javascript yet still follows a mobile-first design philosophy.
        \end{itemize}

        \item \headerrow{\textbf{Recipes}}{\emph{December 2014}}
        \begin{itemize}
            \item Built a MEAN stack database and client-side application for
                managing recipes with MongoDB, Node.js, and Angular.js.  The
                server allows family and friends to add, edit, and comment on
                recipes in one central location, rather than maintaining a long
                list of bookmarks or physical binder.  It's designed for mobile
                use and easy to use from the kitchen.
        \end{itemize}

        \item \headerrow{\textbf{Glorb}}{\emph{Spring 2013}}
        \begin{itemize}
            \item With my wife, designed and prototyped a science education
                project for MIT\@.  Glorbs are a whiffle ball containing a
                circuit with an AVR ATmega, an accelerometer, a lithium-ion
                battery pack, and a bunch of RGB LEDs.  The LEDs change color
                in response to acceleration -- red for freefall, blue for high
                acceleration.  The goal is to explore physics and principles of
                acceleration by playing catch with them.  Glorbs give learners
                concrete visual feedback about the acceleration forces on a
                ball during the course of normal play.  We presented this at
                the MIT Media Lab's Other Festival in Spring 2013.
        \end{itemize}

        \item \headerrow{\textbf{Motion Lights}}{\emph{2013}}
        \begin{itemize}
            \item With spare PIR motion sensors and AVR chips, prototyped a
                power-efficient motion-triggered relay with AA batteries and
                tunable delay before shutoff.  This is small enough to fit in a
                junction box behind a lightswitch.  The lightswitch being on
                the wrong side of the kitchen is no longer an issue.
        \end{itemize}
    \end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Interests}
\begin{itemize*}
    \item Spare Time
        \begin{itemize*}
            \item Hiking, camping, and outdoorsmanship, visiting national parks
            \item Nature and candid photography with Canon Rebel
            \item Recycling broken computers for my servers
            \item Experimenting with new operating systems and frameworks on the
                weekend
            \item Following tech news and podcasts, particularly security news
            \item Participating in Usenet and anonymous darknet projects
            \item Taking things apart to see how they work
        \end{itemize*}
    \item My Workspace
        \begin{itemize*}
            \item Everything running BSD, tiling window manager, Vim, command
                line tools, Screen/Tmux, standing desk, multiple monitors,
                Kinesis Advantage keyboard.
            %\item BSD servers hosting all essential services, including code
                %repositories, databases, and backups
            %\item A dedicated development server for testing
            %\item A Linux or BSD workstation, running a tiling window manager
            %\item Vim for editing, Git for version control, Mutt for mail,
                %chat over IRC
            %\item Standing desk with multiple monitors and Kinesis Advantage
                %keyboard
            %\item Screen or Tmux whenever working over SSH
            %\item Documentation and reports rendered in \LaTeX\ and kept under
                %version control
            %\item Command line tools wherever possible
        \end{itemize*}
        %\item[Open Source Contributions:]
\end{itemize*}
\end{document}
