% Randy Westlund's Personal Resume

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% For \textbullet.
\usepackage{textcomp}
% A different font.
\usepackage{tgpagella}
% Advanced options for lists.
\usepackage{enumitem}
% For left and right aligning text.
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{url}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}
\setlength{\parindent}{0pt}
% Adjust list spacing.
\setlist{itemsep=2pt,topsep=0pt,parsep=0pt}

% Format two pieces of text; one left aligned and one right aligned.
\newcommand{\headerrow}[2]{%
    \begin{tabularx}{\linewidth}{Xr}
	    #1 & #2 \\
    \end{tabularx}
}

\begin{document}
\begin{center}
{\LARGE \textbf{Randy Westlund}}

605 E 21st Ave \ \ \textbullet \ \ Post Falls, ID 83854 \\
(704) 526 5337 \ \ \textbullet \ \ rwestlun@gmail.com \\
\end{center}

\vspace{-4pt}
\hrule
\vspace{-0.8em}
\subsection*{Experience}
  \headerrow{\textbf{Kootenai Strong}}{\textbf{Post Falls, ID}}
	\headerrow{\textit{Co-Founder and President}}{\textit{August 2022--Present}}
    \begin{itemize}[label=--]
        \item Jointly founded a nonprofit focused on Kootenai County which is a combination of think tank and community event organizer. Many details are still TBD.
	\end{itemize}

  \headerrow{\textbf{Westlund Investments \& Property Management}}{\textbf{Post Falls, ID}}
	\headerrow{\textit{Minority Owner and Manager}}{\textit{September 2021--Present}}
    \begin{itemize}[label=--]
        \item Directed investment in Kootenai County single-family homes. Personally managed four properties.
	\end{itemize}

	\headerrow{\textbf{Diligens Technology}}{\textbf{Post Falls, ID}}
	\headerrow{\textit{Co-Founder and CEO}}{\textit{March 2021--Present}}
    \begin{itemize}[label=--]
        \item Created a custom software development business with a focus on web-based technologies.
          Took the technical lead role, designing system architecture and keeping projects on schedule.
	\end{itemize}

	\headerrow{\textbf{Awning Tracker}}{\textbf{Post Falls, ID}}
	\headerrow{\textit{Founder and CEO}}{\textit{July 2016--Present}}
    \begin{itemize}[label=--]
        \item Created a business providing project management
            software to small companies in the awning industry.

        \item Gave presentations and managed booths at international trade shows. Trained multiple interns.
	\end{itemize}

    \headerrow{\textbf{Experimeta, LLC}}{\textbf{Medford, MA}}
    \headerrow{\textit{Co-Founder and CEO}}{\textit{July 2015--August 2018}}
    \begin{itemize}[label=--]
        \item Designed and implemented a second iteration of the firmware and
            software for the ultraviolet cleaning devices described under SPI
            Team, below. Traveled to Kansas to demo and install the improved units.
    \end{itemize}

    \headerrow{\textbf{Earth, Atmospheric, and Planetary Sciences Department, MIT}}
        {\textbf{Cambridge, MA}}
    \headerrow{\textit{System Architect, Researcher}}{\textit{April 2014--May 2017}}
    \begin{itemize}[label=--]
        \item Took over development of SLOOP, an animal biometrics engine which uses image recognition to help
          biologists identify individual members of a species from photographs in order to model population over time.

        \item Traveled solo to New Zealand to upgrade and relocate the Department of Conservation's existing software.
    \end{itemize}

    \headerrow{\textit{Systems Engineer via E5 Aeronautics}}
        {\textit{July 2013--November 2017}}
    \begin{itemize}[label=--]
        \item Designed embedded systems and communication protocols for small unmanned aircraft for civilian use.

        \item Tested unmanned aerial systems (UAS/UAV) at Popocatépetl, an active
            volcano in Mexico. Flew aircraft through the volcano's plume to collect environmental data.
    \end{itemize}

    \headerrow{\textbf{Urban Scholars, University of Massachusetts Boston}}
		{\textbf{Boston, MA}}
	\headerrow{\textit{Robotics Instructor}}{\textit{June 2013--Dec 2013}}
    \begin{itemize}[label=--]
        \item Designed and taught courses on robotics and programming for students aged 11--16.
	\end{itemize}

	\headerrow{\textbf{SPI Team, LLC}}{\textbf{Highland, MD}}
	\headerrow{\textit{Co-Founder and Lead Engineer}}
		{\textit{Feb 2012--June 2013}}
    \begin{itemize}[label=--]
        \item Led a team that designed and implemented embedded electronics and algorithms to control robotic arms.

        \item Collaborated with a patent holder for an autonomous
          internet-connected germicidal ultraviolet light cleaning device. Implemented a functional prototype from
          patent filings, including circuit and firmware design.
	\end{itemize}

	\headerrow{\textbf{NASA Goddard Space Flight Center}}{\textbf{Greenbelt, MD}}
	\headerrow{\textit{Apprentice/Lead Intern, Robotics Engineering Boot Camp}}
		{\textit{June 2011--Aug 2011}}
    \begin{itemize}[label=--]
        \item Designed and implemented a software-defined radio (SDR) to
          receive and decode satellite communications from NOAA's weather satellites.

        \item Traveled to McMurdo, Antarctica and replaced old analog
            equipment with my SDR in December 2011. Returned in December 2012 for follow-up. Learned antarctic
            survival and igloo design.
	\end{itemize}

	\headerrow{\textbf{Charlotte Tent and Awning Co., Inc.}}{\textbf{Charlotte, NC}}
	\headerrow{\textit{Bookkeeper/Assistant}}{\textit{June 2005--Sept 2009}}
    \begin{itemize}[label=--]
        \item Managed accounts receivable and accounts payable for company with \$2.5 million in revenue.
	\end{itemize}

\vspace{2pt}
\hrule
\vspace{-0.8em}
\subsection*{Education}
	\headerrow{\textbf{The University of North Carolina at Charlotte}}
		{\textbf{Charlotte, NC}}
	\headerrow{\textit{B.S., Computer Engineering}}{\textit{2011}}
		\textit{Minor: Mathematics, Classical Studies} \\

\end{document}
% vim:set spell:
